Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-03-18 reports/rmarkdown/manuscript/manuscript_template.Rmd

# I usually load my libraries up front to keep things organized
library(bookdown)
library(knitr)
library(kableExtra)
library(dplyr)
library(tidyverse)
library(igraph)
library(phyloseq)
library(vegan)
library(gridExtra)
library(rafalib)
library(scales)
library(dendextend)
library(edgeR)
remotes::install_github("czarnewski/niceRplots",force=T)
library(niceRplots)

@@

# separate tissue from CVLv2 samples in the second Boston run
CVLv2 <- ps_filt[["boston_r2"]] %>% subset_samples(., Sample_type == "CVL" & Visit == 2) 
tissue <- ps_filt[["boston_r2"]] %>% subset_samples(., Sample_type == "tissue" & Visit == 3)

@@

# Get rarefaction curves
raremax <- map(seqtabs, ~min(rowSums(.x)))
rare_runs <- map2(seqtabs, raremax, ~ .x %>%
             rarecurve(., step = 20, sample = .y, 
                       label = FALSE#,col = col, lty = lty,
          )
)

@@

  # Coerce data into "long" form.
  rare_df <- imap_dfr(rare_obj, ~ .x %>%
              as_tibble(., rownames = "Sample size") %>%
              mutate(Sample = .y) %>%
              mutate(`Sample size` = as.numeric(gsub("N","",`Sample size`)))
  )
  # Get nr. of counts in each sample 
  c <- formatC(count, format="f", big.mark = " ", digits=0)
  rare_df_col <- rare_df %>%
    rename(ASV = "value") %>%
    group_by(Sample) %>% 
    nest() %>%
    mutate(Counts = map(data, ~max(.$`Sample size`))) %>%
    unnest(c(data, Counts)) %>%
    mutate(Counts = ifelse(Counts > count, paste0(">", c), paste0("<", c)))

@@

# Extract data frame from the rarecurve object
rare_df_col<- map2(rare_runs, count, ~ggplot_df_fun(.x, .y))
# Create Plot 
rare_plot <- map2(rare_df_col, raremax, 
              ~ggplot(.x, aes(x = `Sample size`, y = ASV)) +
              theme_bw() +
              scale_color_manual(values=c('tomato', alpha('black', 0.1))) + 
              geom_line(aes(color = Counts, group = Sample)) +
              theme(plot.title = element_text(hjust = 0.5))
            )

r_plot <- pmap(list(rare_plot, raremax, limit, title),
               ~ ..1 + xlim(c(0,..3)) +
               labs(title=paste0("Rarefaction Curve ", ..4)) +
               geom_vline(xintercept = ..2, 
                          linetype='dashed', 
                          color='slategray' )
)

@@

grid.arrange(
  r_plot[[1]],
  r_plot[[3]],
  r_plot[[4]],
  r_plot[[5]],
  nrow = 4,
  #height = c(1, 1, 1, 1),
  clip = FALSE
)
```

>>>>

# I usually load my libraries up front to keep things organized
library(bookdown)
library(knitr)
library(kableExtra)
library(dplyr)
library(tidyverse)
library(igraph)
library(phyloseq)
library(vegan)
library(ggpubr)
library(rafalib)
library(scales)
library(dendextend)
library(edgeR)
remotes::install_github("czarnewski/niceRplots",force=T)
library(niceRplots)

@@

# separate tissue from CVLv2 samples in the second Boston run
CVLv2 <- ps_filt[["boston_r2"]] %>% subset_samples(., Sample_type == "CVL" & Visit == "v2")
tissue <- ps_filt[["boston_r2"]] %>% subset_samples(., Sample_type == "tissue" & Visit == "v3")

@@

# Get rarefaction curves
rare_runs <- map(seqtabs, ~ .x %>%
             rarecurve(., step = 20, label = FALSE)
)

@@

  # Coerce data into "long" form.
  rare_df <- imap_dfr(rare_obj, ~ .x %>%
              as_tibble(., rownames = "Sample size") %>%
              mutate(Sample = .y) %>%
              mutate(`Sample size` = as.numeric(gsub("N","",`Sample size`)))
  )
  # Get nr. of counts in each sample
  c <- formatC(count, format="f", big.mark = " ", digits=0)
  rare_df_col <- rare_df %>%
    dplyr::rename(ASV = "value") %>%
    group_by(Sample) %>%
    nest() %>%
    mutate(Counts = map(data, ~max(.$`Sample size`))) %>%
    unnest(c(data, Counts)) %>%
    mutate(Counts = ifelse(Counts > count, paste0(">", c), paste0("<", c)))

@@

# Extract data frame from the rarecurve object
rare_df_col<- map2(rare_runs, count, ~ggplot_df_fun(.x, .y))
# Create Plot
rare_plot <- map(rare_df_col,
              ~ggplot(.x, aes(x = `Sample size`, y = ASV)) +
              theme_bw() +
              scale_color_manual(values=c('tomato', alpha('black', 0.1))) +
              geom_line(aes(color = Counts, group = Sample)) +
              theme(plot.title = element_text(hjust = 0.5),
                    plot.margin=unit(c(0,0,0.5,0),"cm"))
            )
raremax <- map(seqtabs, ~min(rowSums(.x)))
r_plot <- pmap(list(rare_plot, raremax, limit, title),
               ~ ..1 + xlim(c(0,..3)) +
               labs(title=paste0("Sequencing ", ..4)) +
               geom_vline(xintercept = ..2,
                          linetype='dashed',
                          color='slategray' )
)

@@

```{r Print rare curves, fig.width=6, fig.height=10, fig.align="center"}
ggarrange(r_plot[[1]] + theme(axis.title.x=element_blank()),
          r_plot[[3]] + theme(axis.title.x=element_blank()),
          r_plot[[4]] + theme(axis.title.x=element_blank()),
          r_plot[[5]],
          ncol = 1,
          labels = c("A","B","C","D")
          )
```

**Supp. Figure 10. Rarefraction curves**. **A** Boston 1 sequencing run, **B** Sthlm sequencing run and **C** and **D** shows Boston sequencing run 2 split in two plots showing the CVL visit 2 samples and the the TISSUE visit 3 samples respectively
